### 2015-09-09 approach.tex
Cleaning up.

A high level description of our approach is outlined in \FG{fig:pipeline}. From the oriented surface samples, we construct the approximation $\vec{V}(\vx)$ using our variational formulation. We then apply FIR filters to the coefficients of the approximation to construct a scalar field representing the approximate divergence of the smoothed normal field (\FG{fig:pipeline}c.) We then use an appropriate discretization of the inverse Laplacian operator to solve the Poisson equation \EQ{eq:poisson}, and obtain a smooth function that approximates the original indicator function (\FG{fig:pipeline}c). Our code is also freely available for download.

\subsection{Obtaining the smoothed vector field} \label{sec:getting_vd}
\label{sec:obtainingV}
We define the vector field as $\vec{V}(\vx):=\mathbf{L} \left[\upsilon_1(\vx) \ \upsilon_2(\vx) \ \upsilon_3(\vx)\right]^T$ where $\mathbf{L := [b_1 \ b_2 \ b_3]}$ is a basis for $\realn^3$ that contains the principal lattice directions of the chosen lattice. Each $\upsilon_i$ is a scalar function representing the projection of the smoothed normal field onto each respective principal lattice direction $\mathbf{b}_i$. This may seem unintuitive at first, however, using a non-canonical basis to represent $\vec{V}$ will be convenient in two ways. Firstly, it will allow us to approximate the divergence of $\vec{V}$ by taking directional derivatives of $\vec{V}$ in the principal lattice directions. This is motivated by the fact that it is more natural to approximate derivatives in the principal lattice directions on non-Cartesian lattices. Secondly, it will allow us to construct divergence of the smoothed normal field from more than three principal lattice directions. We also allow each function $\upsilon_i$ to potentially be represented in different function spaces, i.e. {\small 
\begin{equation} 
	\upsilon_i(\vx) = \sum_{k=0}^N \text{v}_k^i \varphi_k^i(\vx) \in \aspace{\lattice{L}}{\varphi^i}.
\end{equation}}
The coefficient vector of $\upsilon_i$ is denoted as $\mathbf{v}_i:=\left[\text{v}_1^i \ \cdots \ \text{v}_N^i \right]$.We use the unfortunate notation $\text{v}_j^i, \varphi_k^i$ to denote that those objects belong to $\upsilon_i(x)$, not to denote exponentiation. We consider each component of $\vec{V}(\vx)$ separately, thus, it suffices to describe the process at one $\upsilon_i$. We simply find the $\upsilon_i$ that minimizes {\small 
\begin{equation} \label{eq:vari_eqn}
 	\sump_{\forall (\vx,\vn) \in P }^{M} (\upsilon_i(\vx) - (\mathbf{L}^{-1})_i \cdot \vect{n})^2 + E(\upsilon_i).
\end{equation} }
Where $(\mathbf{L}^{-1})_i$ is the $i^{th}$ column of $(\mathbf{L}^{-1}).$ As before, this provides us with a parametrized way of controlling the smoothness of the resulting approximation, without the need to explicitly choose a smoothing kernel. These $\mathbf{v}_i$ can be obtained using the procedure of \SC{sec:vari_review}.

@@

\subsubsection{Shifted Reconstruction Spaces}
To reconstruct within a shifted space, the input point-set is shifted by $\frac{1}{2}\mathbf{b_i}$ then reconstructed within $\fspce{\varphi}{L}$. This is clearly equivalent to reconstructing in a shifted basis space, however, care must be taken to ensure that the data are brought back to a centered representation. Our choice of a shifted derivative filter $s[n]$ accounts for this and brings the resulting approximation back to the unshifted space. Both the shifted and unshifted filters we utilize are found in \TA{tab:filters} and are chosen so that they provide a fourth-order discretization of the 1D derivative operator~\cite{gradrev}.

\subsubsection{Four Direction Divergence on the BCC Lattice}
It is also possible to consider a basis $\mathbf{L}$ in which we choose more than three principal directions to reconstruct the divergence. Thus, we may choose $\mathbf{L} = \mathbf{\Xii_{B}} $ as the basis for our function. To accommodate for this, we redefine $\vec{V}(\vx):=\mathbf{L} \left[\upsilon_1 \ \upsilon_2 \ \upsilon_3 \ \upsilon_4 \right.]^T$ Since this matrix is not square, it is not possible to take its inverse in \EQ{eq:vari_eqn}. Instead, the least norm inverse $\mathbf{L^T(LL}^T\mathbf{)}^{-1}$ is used. It is easy to see that, by the same reasoning as in equation \EQ{eq:div_dir}, $\grad \cdot \vec{V} = \dv{\mathbf{b_1}}\upsilon_1 + \dv{\mathbf{b_2}}\upsilon_2 + \dv{\mathbf{b_3}}\upsilon_3 + \dv{\mathbf{b_4}}\upsilon_4$. Thus, we may use the same idea as in the three direction case, approximating each direction separately, and summing the coefficients to obtain an approximation to the divergence (the shifted case is also similar).

>>>>

A high level description of our approach is outlined in \FG{fig:pipeline}. 
From the oriented surface samples, we construct the approximation $\vec{V}(\vx)$ using our variational formulation. 
We then apply FIR filters to the coefficients of the approximation to construct a scalar field representing the approximate divergence of the smoothed normal field (\FG{fig:pipeline}c.) 
Using appropriate discretization of the inverse Laplacian operator we then solve the Poisson equation \EQ{eq:poisson}, and obtain a smooth function that approximates the original indicator function (\FG{fig:pipeline}c). 
Our code is also freely available for download.

\subsection{Obtaining the smoothed vector field} \label{sec:getting_vd}
\label{sec:obtainingV}
We define the vector field as $\vec{V}(\vx):=\mathbf{L} \left[\upsilon_1(\vx) \ \upsilon_2(\vx) \ \upsilon_3(\vx)\right]^T$ where $\mathbf{L := [b_1 \ b_2 \ b_3]}$ is a basis for $\realn^3$ that contains the principal lattice directions of the chosen lattice.
Each $\upsilon_i$ is a scalar function representing the projection of the smoothed normal field onto each respective principal lattice direction $\mathbf{b}_i$. 
This may seem unintuitive at first, however, using a non-canonical basis to represent $\vec{V}$ will be convenient in two ways. 
Firstly, it will allow us to approximate the divergence of $\vec{V}$ by taking directional derivatives of $\vec{V}$ in the principal lattice directions. 
This is motivated by the fact that it is more natural to approximate derivatives in the principal lattice directions on non-Cartesian lattices. 
Secondly, it will allow us to construct divergence of the smoothed normal field from more than three principal lattice directions. 
We also allow each function $\upsilon_i$ to potentially be represented in different function spaces, i.e. {\small 
\begin{equation} 
	\upsilon_i(\vx) = \sum_{k=0}^N \text{v}_k^i \varphi_k^i(\vx) \in \aspace{\lattice{L}}{\varphi^i}.
\end{equation}}
The coefficient vector of $\upsilon_i$ is denoted as $\mathbf{v}_i:=\left[\text{v}_1^i \ \cdots \ \text{v}_N^i \right]$.
We use the unfortunate notation $\text{v}_j^i, \varphi_k^i$ to denote that those objects belong to $\upsilon_i(x)$, not to denote exponentiation. 
We consider each component of $\vec{V}(\vx)$ separately, thus, it suffices to describe the process at one $\upsilon_i$. 
We simply find the $\upsilon_i$ that minimizes {\small 
\begin{equation} \label{eq:vari_eqn}
 	\sump_{\forall (\vx,\vn) \in P }^{M} (\upsilon_i(\vx) - (\mathbf{L}^{-1})_i \cdot \vect{n})^2 + E(\upsilon_i).
\end{equation} }
Where $(\mathbf{L}^{-1})_i$ is the $i^{th}$ column of $(\mathbf{L}^{-1}).$ 
As before, this provides us with a parametrized way of controlling the smoothness of the resulting approximation, without the need to explicitly choose a smoothing kernel. 
These $\mathbf{v}_i$ can be obtained using the procedure of \SC{sec:vari_review}.

@@

\subsubsection{Shifted Reconstruction Spaces}
To reconstruct within a shifted space, the input point-set is shifted by $\frac{1}{2}\mathbf{b_i}$ then reconstructed within $\fspce{\varphi}{L}$. 
This is equivalent to reconstructing in a shifted basis space, however, care must be taken to ensure that the data are brought back to a centered representation. 
Our choice of a shifted derivative filter $s[n]$ accounts for this and brings the resulting approximation back to the unshifted space. 
Both the shifted and unshifted filters we utilize are found in \TA{tab:filters} and are chosen so that they provide a fourth-order discretization of the 1D derivative operator~\cite{gradrev}.

\subsubsection{Four Direction Divergence on the BCC Lattice}
It is also possible to consider a basis $\mathbf{L}$ in which we choose more than three principal directions to reconstruct the divergence. 
Thus, we may choose $\mathbf{L} = \mathbf{\Xii_{B}} $ as the basis for our function. 
To accommodate for this, we redefine $\vec{V}(\vx):=\mathbf{L} \left[\upsilon_1 \ \upsilon_2 \ \upsilon_3 \ \upsilon_4 \right.]^T$ 
Since this matrix is not square, it is not generally possible to take its inverse in \EQ{eq:vari_eqn}. 
Instead, the least norm inverse $\mathbf{L^T(LL}^T\mathbf{)}^{-1}$ is used. 
It is easy to see that, by the same reasoning as in equation \EQ{eq:div_dir}, $\grad \cdot \vec{V} = \dv{\mathbf{b_1}}\upsilon_1 + \dv{\mathbf{b_2}}\upsilon_2 + \dv{\mathbf{b_3}}\upsilon_3 + \dv{\mathbf{b_4}}\upsilon_4$. 
Thus, we may use the same idea as in the three direction case, approximating each direction separately, and summing the coefficients to obtain an approximation to the divergence (the shifted case is also similar).

### 2015-09-09 conclusion.tex
Cleaning up.

\subsection{Robustness}
When the input data contain noise, our method allows us to choose an appropriate smoothing parameter $\lambda_2$ to average out said error. However, our method fails to be as robust as the Screened Poisson algorithm when the data are non-uniform. We speculate that this is due to the fact that we employ no heuristics to account for the deviation from the assumption of uniformity (\FG{fig:r2}.)

@@

\subsection{Parameter Selection}
In our experiments, choosing $\lambda_2$ to be small reduced smoothing as expected. However, we observed that when $\lambda_2$ passed below a threshold, the surface began to show ringing or aliasing artifacts. This is somewhat to be expected, as choosing a very thin smoothing will cause the approximation \EQ{eq:vdef} to break down. Additionally, the choice of $\lambda_1$, the compactness constraint, didn't seem to effect the solution much, it's only effect was on the choice of the parameter $\lambda_2$. That is, when $\lambda_1$ was large, $\lambda_2$ had to be large to obtain similar smooth solutions.

The parameterized nature of our solution allows us to control the degree to which the initial data are smoothed. However, this also makes it difficult to conclusively compare methods. More investigation and exploration of the parameter space is required. Moreover, there also appears to be a point at which choosing $\lambda_2$ to be too small introduces aliasing artifacts.

>>>>

\subsection{Robustness}
When the input data contain noise, our method allows us to choose an appropriate smoothing parameter $\lambda_2$ to average out said error. 
However, our method fails to be as robust as the Screened Poisson algorithm when the data are non-uniform. 
We speculate that this is due to the fact that we employ no heuristics to account for the deviation from the assumption of uniformity (\FG{fig:r2}).

@@

\subsection{Parameter Selection}
In our experiments, choosing $\lambda_2$ to be small reduced smoothing as expected. 
However, we observed that when $\lambda_2$ passed below a threshold, the surface began to show ringing or aliasing artifacts. 
% What do I mean here? This is also very awkward...
This is somewhat to be expected, as choosing a very thin smoothing will cause the approximation \EQ{eq:vdef} to break down. 
Additionally, the choice of $\lambda_1$, the compactness constraint, didn't seem to effect the solution much, it's only effect was on the choice of the parameter $\lambda_2$. 
That is, when $\lambda_1$ was large, $\lambda_2$ had to be large to obtain similar smooth solutions.

The parameterized nature of our solution allows us to control the degree to which the initial data are smoothed.
However, this also makes it difficult to conclusively compare methods. 
More investigation and exploration of the parameter space is required. 
Moreover, there also appears to be a point at which choosing $\lambda_2$ to be too small introduces aliasing artefacts.

### 2015-09-09 introduction.tex
Cleaning up.

\label{sec:intro}
Reconstructing a solid model from a scattered set of points is a common and well studied problem in computer graphics. Interest in this problem is rooted in the desire to convert real life data-sets -- data acquired from range scanners and now increasingly from commodity hardware like the Kinect -- to 3D polygonal models. The idea also has a applications in model re-meshing and mesh hole filling, when one has a poorly formatted mesh and would like a better representation of it.

Given an oriented point-set, a common approach is to find an implicit function whose iso-contour corresponds to an approximation of the original surface. In this work we take a ``signal processing'' approach to this problem -- we cast the problem into a general shift-invariant setting. More explicitly, we reconstruct the desired implicit function within a function space spanned by lattice translates of a single generating function. The extension to this class of function spaces allows us to consider anchoring our basis functions at non-Cartesian lattice sites (\SC{sec:smpl_review}). Our approach is general and applicable to any valid lattice and generator, but our implementation is narrowed to applicable function spaces over the \emph{Body Centred Cubic} (BCC) and \emph{Cartesian} (CC) lattices.

@@

The advantage of moving to the BCC lattice is two fold. First, it's well known that the BCC lattice generates the optimal sampling pattern in $\realn^3$. The argument for optimality is simple; the sampling of a function with respect to the BCC lattice is equivalent to a periodization of it's frequency spectrum about the BCC's dual lattice, the \emph{Face Centered Cubic} (FCC) lattice. Optimality follows from the observation that the FCC lattice is the optimal sphere packing lattice in three dimensions, that is, it packs frequency replica as tightly as possible in the Fourier domain, resulting in less \emph{pre-aliasing} from sampling. For isotropically band-limited functions, this tighter packing of frequency content allows for about 30\% more information to be captured when compared to samplings generated from a Cartesian lattice. The second advantage to moving to the BCC lattice is that there exist reconstruction filters on the BCC lattice that outperform commonly used filters of equivalent order on the CC lattice in terms of both speed and accuracy \cite{practicalbox} (in software implementations) -- these filters are also more compact than their typical CC counterparts. In the context of our surface reconstruction scheme, this gives rise to regularization matrices that are more sparse on the BCC lattice and tend to provide faster convergence when optimizing the initial point set (\SC{sec:vari_review}).

Our surface reconstruction methodology follows the general Poisson approach, but with a few twists. First, we construct a smoothed approximation to the gradient field of a model's indicator function. The divergence of the gradient field is estimated and subsequently fed into a Poisson solver that outputs the coefficients needed to approximate the smoothed indicator function in a target shift invariant space. This Poisson solver is tailored to cater to the approximation power provided by each space. However, our approach is novel in two notable ways. Firstly, we employ a variational scheme to obtain a lattice-based approximation of the gradient field. This scheme depends only on the generating kernel of the target space and optimizes a functional that incorporates interpolation and smoothness constraints. Secondly, we utilize the theory behind shift-invariant spaces to seek discretizations of the divergence and Laplacian operators that are tailored to exploit the full approximation capabilities of the target space.

>>>>

\label{sec:intro}
Reconstructing a solid model from a scattered set of points is a common and well studied problem in computer graphics. 
Interest in this problem is rooted in the desire to convert real life data-sets -- data acquired from range scanners and now increasingly from commodity hardware like the Kinect -- to 3D polygonal models. 
It also has applications in model re-meshing and mesh hole filling, when one has a poorly structured mesh and would like a better representation of it.

Given an oriented point-set, a common approach is to find an implicit function whose iso-contour corresponds to an approximation of the original surface. 
In this work we take a ``signal processing'' approach to this problem -- we cast the problem into a general shift-invariant setting. 
More explicitly, we reconstruct the desired implicit function within a space spanned by lattice translates of a single generating function. 
The extension to this class of function spaces allows us to anchor our basis functions at non-Cartesian lattice sites (\SC{sec:smpl_review}). Our approach is general and applicable to any valid lattice and generator, but our implementation is narrowed to applicable function spaces over the \emph{Body Centred Cubic} (BCC) and \emph{Cartesian} (CC) lattices.

@@

The advantage of moving to the BCC lattice is two fold. 
First, it's well known that the BCC lattice generates the optimal sampling pattern in $\realn^3$. 
The argument for optimality is simple; the sampling of a function with respect to the BCC lattice is equivalent to a periodization of it's Fourier frequency spectrum about the BCC's dual lattice, the \emph{Face Centered Cubic} (FCC) lattice.
Optimality follows from the observation that the FCC lattice is the optimal sphere packing lattice in three dimensions, that is, it packs frequency replica as tightly as possible in the Fourier domain, resulting in less \emph{pre-aliasing} from sampling. 
For isotropically band-limited functions, this tighter packing of frequency content allows for about 30\% more information to be captured when compared to samplings generated from a Cartesian lattice.
The second advantage to moving to the BCC lattice is that there exist reconstruction filters on the BCC lattice that outperform commonly used filters of equivalent order on the CC lattice in terms of both speed and accuracy \cite{practicalbox} (in software implementations) -- these filters are also more compact than their typical CC counterparts. 
In the context of our surface reconstruction scheme, this gives rise to regularization matrices that are more sparse on the BCC lattice and tend to provide faster convergence when optimizing the initial point set (\SC{sec:vari_review}).

Our surface reconstruction methodology follows the general Poisson approach, but with a few twists. 
First, we construct a smoothed approximation to the gradient field of a model's indicator function. 
We then estimate the divergence of that gradient field and feed it into a Poisson solver that outputs the coefficients needed to approximate the smoothed indicator function in a target shift invariant space. 
This Poisson solver is tailored to cater to the approximation power provided by each space. 
However, our approach is novel in two notable ways. 
Firstly, we employ a variational scheme to obtain a lattice-based approximation of the gradient field. 
This scheme depends only on the generating kernel of the target space and optimizes a functional that incorporates interpolation and smoothness constraints. 
Secondly, we utilize the theory behind shift-invariant spaces to seek discretizations of the divergence and Laplacian operators that are tailored to exploit the full approximation capabilities of the target space.

### 2015-09-09 poisson_errker.tex
Cleaning up.

Suppose we are given an $L_2(\ucube^s)$ function $\rho(
\vect{x})$ that is
defined on the open unit cube $\oucube^s$. In order to obtain a
Fourier sine series that converges to $\rho$ almost everywhere in
$\oucube^s$, we need to extend $\rho$ periodically such that it is odd
with respect to each variable. Particularly, let us extend the domain
of $\rho$ so that, within the interval $\cube^s$, it satisfies
{\small
\begin{equation}  
 \rho(\vect{x}) :=  
\begin{cases}
\bigl( \prod_{i=1}^s \sgn(x_i) \bigr)
\rho(|x_1|, \ldots, |x_s| ) &\mbox{if } \forall i \; |x_i| \ne 0 \\ 
0 &\mbox{otherwise},
\end{cases}
\label{eq:oddextension}
\end{equation}
}

while outside $\cube^s$, it is $\cube^s$-periodic, i.e. $\rho(\vect{x}
+ 2\vect{k}) = \rho(\vect{x})$ for $\vect{k} \in \ints^s$. The
extended function $\rho$ can be developed into a multidimensional
Fourier sine series, the coefficients of which are given by 
\begin{equation}
  \st{\rho}[\vect{m}] = 2^s \innerproduct{\rho(\vect{x})}
  {\textstyle{\prod_{i=1}^s}\sin(m_i\pi x_i)}, \; \text{for}\; \vect{m} \in \ints^s_+.
\end{equation}
The coefficient sequence $\st{\rho}[\vect{m}]$ can also be seen as a
special case of the more general multidimensional Fourier
series. In fact, with an odd extension of the sequence $\st{\rho}$, the
function $\rho$ can be expressed as a Fourier series. In particular,
if we define the Fourier series coefficients $\ft{\rho}[\vect{m}]$
(for $\vect{m} \in \ints^s$) as
{\small \begin{equation}
	\ft{\rho}[\vect{m}] := 
	\begin{cases}
	\frac{1}{(2\imath)^{s}} \prod_i \sgn(m_i)
	\st{\rho}[|m_1|,\ldots,|m_s|] &\mbox{if } \forall i \; |m_i| \ne 0 \\
	0 &\mbox{otherwise},
	\end{cases}
	\label{eq:oddFourierExtension}
\end{equation}}

@@

In many approximation scenarios, one typically assumes a Dirac point sampling
model, i.e. $\analysis{\varphi}(\vect{x}) = \delta(\vect{x})$.
This prevents the direct realization of the minimum approximation scenario.
Furthermore, for many functions encountered in practice, the power spectrum is
concentrated around $\vect{\omega} = 0$. For such scenarios, one speaks of an
\emph{asymptotically optimal} $k$-th order approximation scheme if the $L_2$
error behaves as $O(h^k)$ where $k = \order{\lattice{L}}{\varphi}$. Our operator
discretization approach is also based on these assumptions. Provided that $\chi$ has appropriate smoothness, our goal is to design suitable digital filters that yield %$V \in W_2^k(\cube^s)$, our goal is to design suitable digital filters that yield
$\appf{\chi}$ such that $\LLnorm{\chi - \appf{chi}} = O(h^k)$. %As discussed earlier in~\SC{sec:interpQuasiInterp}, the criterion that needs to be satisfied is $E_{\mathsf{mod}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2k})$.

\subsection{Relationship to the Galerkin method}
\label{sec:Galerkin}
The modified residue error kernel~\eqref{eq:opResidue} can also be analyzed in light of the Galerkin method~\cite{quarteroni08} using a weak formulation of the Poisson equation~\eqref{eq:PoissonEquation}, where the trial and test spaces are the same with the notable difference that the spaces are not required to explicitly satisfy any particular boundary conditions. Rather, a zero boundary condition is implicitly obtained by requiring that the solution coefficients $c[\cdot]$ be odd. % as explained in~\SC{sub:approximatesol}. 
Here, we establish the connection for the homogeneous case but the analysis also easily extends to the non-homogeneous case, as well as to other types of differential operators.

@@

On the other hand, if the point samples of $f$ are already available (i.e. $\analysis{\varphi} = \delta$) and the orthogonal projection cannot be realized, then the goal of the asymptotically optimal
procedure is to find a suitable correction filter $\gamma$ such that $E_{\mathsf{mod}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2k})$ where $k = \order{\lattice{L}}{\varphi}$.  
%If we define the analysis function
%$\phi(\vect{x}) := \sum_{\vect{k} \in \ints^s} t[\vect{x}]
%\delta(\vect{k} - \mat{L}\vect{k})$, then the criterion
%$E_{\mathsf{res}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2k})$ is
%equivalent to the requirement that the moments of $\phi$ and
%$\invlaplacian \dual{\varphi}$ (here
%$\ftpairs{\invlaplacian}{(-4\pi^2\norm{\vect{\omega}}^2)^{-1}}$) match
%up to the order $k$, i.e.  $\int_{\reel^s}
%\vect{x}^{\vect{\mu}}(\phi(\vect{x}) - \invlaplacian
%\dual{\varphi}(\vect{x})) d\vect{x} = 0$ for $0 \le \abs{\vect{\mu}} <
%k$. 
In other words, our approximation procedure attempts to reproduce the Galerkin orthogonality condition given by~\eqref{eq:GalerkinOrthogonality}. %This is akin to the quasi-interpolation condition~\eqref{eq:quasiCondition} introduced
in~\SC{sec:interpQuasiInterp}.

>>>>

Suppose we are given an $L_2(\ucube^s)$ function $\rho(\vect{x})$ that is defined on the open unit cube $\oucube^s$. 
In order to obtain a Fourier sine series that converges to $\rho$ almost everywhere in
$\oucube^s$, we need to extend $\rho$ periodically such that it is odd with respect to each variable. 
Particularly, let us extend the domain of $\rho$ so that, within the interval $\cube^s$, it satisfies
{\small
\begin{equation}  
 \rho(\vect{x}) :=  
\begin{cases}
\bigl( \prod_{i=1}^s \sgn(x_i) \bigr)
\rho(|x_1|, \ldots, |x_s| ) &\mbox{if } \forall i \; |x_i| \ne 0 \\ 
0 &\mbox{otherwise},
\end{cases}
\label{eq:oddextension}
\end{equation}
}
while outside $\cube^s$, it is $\cube^s$-periodic, i.e. $\rho(\vect{x} + 2\vect{k}) = \rho(\vect{x})$ for $\vect{k} \in \ints^s$. 
The extended function $\rho$ can be developed into a multidimensional Fourier sine series, the coefficients of which are given by 
\begin{equation}
  \st{\rho}[\vect{m}] = 2^s \innerproduct{\rho(\vect{x})}
  {\textstyle{\prod_{i=1}^s}\sin(m_i\pi x_i)}, \; \text{for}\; \vect{m} \in \ints^s_+.
\end{equation}
The coefficient sequence $\st{\rho}[\vect{m}]$ can also be seen as a special case of the more general multidimensional Fourier series. 
In fact, with an odd extension of the sequence $\st{\rho}$, the function $\rho$ can be expressed as a Fourier series. 
In particular, if we define the Fourier series coefficients $\ft{\rho}[\vect{m}]$
(for $\vect{m} \in \ints^s$) as
{\small \begin{equation}
	\ft{\rho}[\vect{m}] := 
	\begin{cases}
	\frac{1}{(2\imath)^{s}} \prod_i \sgn(m_i)
	\st{\rho}[|m_1|,\ldots,|m_s|] &\mbox{if } \forall i \; |m_i| \ne 0 \\
	0 &\mbox{otherwise},
	\end{cases}
	\label{eq:oddFourierExtension}
\end{equation}}

@@

In many approximation scenarios, one typically assumes a Dirac point sampling model, i.e. $\analysis{\varphi}(\vect{x}) = \delta(\vect{x})$.
This prevents the direct realization of the minimum approximation scenario. 
Furthermore, for many functions encountered in practice, the power spectrum is concentrated around $\vect{\omega} = 0$. 
For such scenarios, one speaks of an \emph{asymptotically optimal} $k$-th order approximation scheme if the $L_2$ error behaves as $O(h^k)$ where $k = \order{\lattice{L}}{\varphi}$. 
Our operator discretization approach is also based on these assumptions. 
Provided that $\chi$ has appropriate smoothness, our goal is to design suitable digital filters that yield  $\appf{\chi}$ such that $\LLnorm{\chi - \appf{chi}} = O(h^k)$.

\subsection{Relationship to the Galerkin method}
\label{sec:Galerkin}
The modified residue error kernel~\eqref{eq:opResidue} can also be analyzed in light of the Galerkin method~\cite{quarteroni08} using a weak formulation of the Poisson equation~\eqref{eq:PoissonEquation}, where the trial and test spaces are the same with the notable difference that the spaces are not required to explicitly satisfy any particular boundary conditions. 
Rather, a zero boundary condition is implicitly obtained by requiring that the solution coefficients $c[\cdot]$ be odd. 
Here, we establish the connection for the homogeneous case but the analysis also easily extends to the non-homogeneous case, as well as to other types of differential operators.

@@

On the other hand, if the point samples of $f$ are already available (i.e. $\analysis{\varphi} = \delta$) and the orthogonal projection cannot be realized, then the goal of the asymptotically optimal
procedure is to find a suitable correction filter $\gamma$ such that $E_{\mathsf{mod}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2k})$ where $k = \order{\lattice{L}}{\varphi}$.

In other words, our approximation procedure attempts to reproduce the Galerkin orthogonality condition given by~\eqref{eq:GalerkinOrthogonality}. %This is akin to the quasi-interpolation condition~\eqref{eq:quasiCondition} introduced in~\SC{sec:interpQuasiInterp}.
